Parallel multi-objective optimization using selective operation application islands

### 2017-06-07 hpmoon-coor.tex
Removed all references to cooperative coevolutionary in our method. Closes #15

\title{Parallel multi-objective optimization using selective operation application
  islands}
% New title suggestion
% Should coevolutionary go somewhere? Are they coevolutionary? - jj
% PABLO: Renaming again to avoid using the coevolutionary and cooperative

@@

A similar idea is presented here to deal with un-decomposable problems: 
instead of sharing parts of individuals, each processor applies the variation 
operators to a specific subset of the whole individual. We have previously proved 
that extending the length of these subsets, and therefore, sharing some search 
space between islands, implies an improvement in the results.

@@

MOPs usually require a high number of variables, meaning that the MOEAs need to deal with large individuals and spent significant extra time for crossover, mutation and migration. Different authors have proposed methods to divide the decision space (the chromosome) to improve the performance and solution quality. In this aspect, the co-evolution model is a dimension-distributed model where a high-dimensional problem is divided into lower dimensional problems \citep{Gong15models,Tonda12cooperative}, and evolved separately. One example of application of this technique was described in \citep{Kimovski15Parallel}. The method presented in that works involves different workers that evolve sub-populations created and recombined by a master process, which performs different recombination alternatives from the parts returned by worker processes. A high dimensional problem was used to compare these
alternatives. In \citep{Dorronsoro13superlinear}, a distributed
coevolutionary island model was used.  Although in both papers
significant speedups were attained, only a low number of nodes were
employed (8). However, when the number of islands is increased, the division
of each section of the chromosome becomes smaller, and the scalability
may be affected by obtaining lower quality solutions in the same
amount of time.

@@

In our preliminary work \citep{Garcia16hpmoon} we proved
% tried to or actually did it? What did we prove? FERGU: Done
that,  instead of making every island focus in a disjoint subset of the
chromosome, the usage of overlapped (shared) sections of the
chromosome in a coevolutionary multi-objective island-based algorithm
can improve the quality of the solutions in the same computing time
when the number of islands increases. We discovered that the most
adequate overlapping size may vary depending on a relation between the
number of islands and the individual size. However, the experiments
were conducted in a limited experimental system: mono-processor and synchronous island model. This
motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more complete parameter setting. Besides comparing previous methods in this new experimental setup, in this paper we propose
a new method that automatically adapts the size of the overlapped
sections depending on the number of islands to use, comparing it with the previous versions. 
% We have to
                                % emphasize what is actually done. Is
                                % this an addition to the old paper,
                                % or a complete rewrite? - JJ FERGU: rewritten previous paragraph

@@

The hypothesis of this paper is that using overlapped sections of the
chromosome, calculated depending the number of islands to use, in a
coevolutionary multi-objective island-based algorithm, in a real computational environment, can improve the
quality of the solutions in the same computing time with respect to
the baseline, disjoint and partly overlapped methods. %That was the
                                %hypothesis of the previous
                                %paper. This paper has a new
                                %hypothesis, right? - JJ FERGU: no, this is the hypothesis of this paper (comparing adaptive with partly overlapped), but clarifying it
In order to prove this claim, our new adaptive method has been
compared against different overlapping islands schemes: a
baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a
coevolutionary disjoint section approach version of it and a
fixed-size overlapped version. %What was done in the previous paper?
                               %Are we re-using the results in that
                               %paper? - JJ FERGU: explained before that we are showing new results.
Different benchmark problems and different large number of islands
have been used. Results show that this new technique can improve
different quality indicators in the same amount of time when the
problem size is large.  % Shouldn't this start with "We are trying to
                        % prove..." - JJ FERGU: Already writed in previous paragraph

The rest of the paper is organized as follows: after the State of the Art in distributed and coevolutionary MOEAs, 
the used methodology and the compared algorithms are described in Section \ref{sec:coevo}. 
Then, the results of the experiments are presented (Section \ref{sec:res}), Finally, the conclusions and future work are discussed.

@@

% Is this really cooperative coevolution? - JJ FERGU: You mean the Dorronsoro one? The title says it
Addressing high-dimensional problems with cooperative coevolution has
also been studied in several works with approaches closer to the one
presented here. The approach to focus on a portion of the chromosome,
as in our overlapped method, was firstly used in the work by
Dorronsoro et al. \citep{Dorronsoro13superlinear}, obtaining
super-linear performance 
in several instances. This approach has also been used by Kimovski et al. \citep{Kimovski15Parallel}, but using a
master-slave method that splits the population into several processors. As in previous work, each node
runs a parallel MOEA that only affects some portion of 
the individuals and the master
process receives all the sub-populations to be combined every certain number of generations. Up to 8 processors
were used in the experimental setup, and several
combination alternatives were compared. The main difference of our work with respect to previous works is that our approach does not 
broadcast all solutions to all islands for recombination, but only one solution to a random island, needing less
communication time. Moreover, Dorronsoro or Kimovsky approaches limited the maximum number of islands to 8, while in this paper we have
used up to 128 islands.

@@

In our previous work \citep{Garcia16hpmoon} we used some of
the aforementioned ideas to compare two co-evolutionary dMOEAs. The first
one divided the chromosome in $P$ sections, being $P$ the number of
islands. Every island $p$ only performed the mutation and crossover in
that part ($p_{th}$) of the chromosome, while the fitness was
calculated using the whole individual. After a certain number of
generations, individuals were migrated randomly to other islands. The
performance metrics were calculated at the end of the run. The second
method, coevolution with overlapping islands, used the $p_{th-1}$ and
$p_{th+1}$ sections of each chromosome, besides the $p_{th}$
part. During the same amount of time both methods obtained better
results than a baseline algorithm that dealt with the whole chromosome
in each island for crossover and mutation. We discovered that the
performance using one or another method depends on the number of
sections of the individuals and the number of islands used. This
motivates us to find a new adaptive method to select this number of
sections of the chromosome to use, depending on the number of
islands. Besides, previous experiments were performed on a single
processor synchronous island model with a limited number of islands
(8, 32 and 128). In this paper,  8, 16, 32, 64 and 128 islands have
been used, and this time, the experiments have been run on a real
cluster. Therefore, at the same time we are proposing an adaptive
method to divide the individual search space, we are validating the
previous methods.

@@

\section{Methodology} % This should be called
                                % methodology. The object of the
                                % section is to explain the
                                % methodology used to test the
                                % problem, in order to do that we have
                                % tested different versions that prove
                                % that our methodology works for the
                                % precise reasons we think it works- JJ FERGU: Done, and explained
\label{sec:coevo}

@@

In this paper we analyse several coevolutionary algorithms we have
implemented by using a parallel multi-objective baseline algorithm (B)
as a basis for comparisons. Our proposed methods %methods or method?
                                %Which methods? - JJ
are based in NSGA-II, as almost all the previous works discussed
before
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}. % This is SoA stuff - JJ FERGU: Yes, I added it here againg because a reviewer wasn't very attentive
Therefore, we have used a basic distributed NSGA-II algorithm without
overlapping sections as the baseline (B).

%This probably should deserve a "Algorithm" environment too - JJ FERGU: You mean the LaTeX one? I've used it in the pseudocode figures
This basic distributed algorithms spreads the population among $P$
islands; after a fixed number of generations,
one individual in a given island is migrated to another random island,
thus avoiding to synchronize the global Pareto Front (PF) every
certain number of generations as other methods described in Section 2
do. At the end of the run, the Pareto Fronts of all islands are
aggregated into a new one, and the quality measures are evaluated. 
Different coevolutionary alternatives can be devised to evolve the
subpopulations according to the decision space to be explored by each
islands. Here we will consider three methods in which each island only
performs crossover and mutation in specific sections of the
individuals.

%This algorithm is a regular NSGA-II algorithm distributed along a number $P$ of islands. After a fixed number of generations, one individual is migrated to another random island. At the end of the run, PFs of all islands are aggregated in a new one in order to compute the quality measures. This baseline method has been chosen as it does not require synchronization of the global PF every certain number of generations, as other methods described in Section 2 do.
%% some justification on why this was chosen - JJ PABLO: Added 
%
%% And some liaison to next subsection - JJ
%This method will be compared to different coevolutionary approaches that are similar to the baseline, with the exception on the decision space to explore in each island.
%Three different coevolutionary methods have been used. In all these methods, each island only performs crossover and mutation in specific sections of the individuals.

@@

\subsection{Coevolution with disjoint islands (D)} 
In this approach, each individual of size $L$ is split into $P$ chunks
of size $L/P$. Every island $p$ only performs crossover and mutation
on the $p_{th}$ part of the individuals. Figure \ref{fig:disjoint}
describes this approach.   
%
\begin{figure*}[h!tb]
\centering
\includegraphics[width=12cm]{islandDisjoint.jpg}
\caption{Disjoint algorithm: every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals.}
\label{fig:disjoint}
\end{figure*}

\subsection{Coevolution with overlapping islands (O)}
This approach is similar to the previous one, but every island also uses the $p+1$ and $p-1$ (module size) chunks of the individual for crossover and migration. Therefore, some kind of overlapping of the crossed and mutated parts exists between islands. Figure \ref{fig:overlapping} shows the affected parts of the individuals in
each island.

@@

\subsection{Adaptive coevolution with overlapping islands (A)} 
As in the previous method, the sections to address are overlapped, but
instead using one extra section on each side of the $p$ section ($p+1$
and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$),
being $c$ a value depending on the number of islands.
% That's not adaptive. It's simply variable - JJ FERGU: it depends on the number of islands. What term do you suggest?
As a first
approach to automatically calculate this value the results shown in
\citep{Garcia16hpmoon} have been used as a base to obtain $c$. In that
work, the overlapped method ($c=1$) obtained better results when the
number of islands were $>$8. On the contrary, when the number of
islands is small, no overlapping is necessary. So, we have used this
knowledge to create the formula $c=round(0.2*P-1)/2$ to calculate the
extra sections to overlap. Therefore, when $P=8$ then $c=0$
(equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so
on. Figure \ref{fig:adaptive} explains this method.

@@

%EXPLANATION OF THE RESULTS
This can be explained comparing the number of non-dominated solutions in each island and the average number of generations (Table \ref{tab:sols512} and Table \ref{tab:sols2048}). With both chromosome lengths, increasing the number of islands implies more generations with all the methods (logically, as there are less individuals in each island). But also, the co-evolutionary methods approach to the number of generations with the baseline when increasing the number of islands. However, with $L=2048$ the migration time is enough big to almost not improve the number of generations with respect to the baseline, even in the lower number of islands, as it happens with $L=512$. Therefore, more generations do not necessarily improve the solution of the global PF, but focusing on different elements of the chromosome. As indicated previously, every island is unaware of the other islands PFs, and they are trying to optimize their solutions independently. With respect to the average number of solutions in each island, there is a clear difference in number with the baseline with $L=512$, where this value is in the most of the cases, less than a half. The number of non-dominated solutions also improves a better Spread indicator, where the baseline almost always obtains better values %TENGO QUE COMENTAR MAS LOS RESULTADOS Y ENTENDERLO TODO Y JUSTIFICARLO FINAMENTE

Finally, as happened in \citep{Garcia16hpmoon}, results show that all the quality indicators decrease when the number of islands is increased, as the  sizes of the subpopulations are smaller. This is consistent with the claim by Dorronsoro et al. \citep{Dorronsoro13superlinear}, who found that cooperative coevolutionary MOEAs work better on bigger populations (more than 100 individuals).

@@

High-performance problems % problems are not high-performance. They
                          % _require_ high performance
 that require a large number of decision variables can leverage the
 division of the decision space that parallel and distributed
 algorithms imply. This can be done in dMOEAs by dividing the
 chromosome into different parts, each one modified by a different
 island. This paper compares a baseline distributed NSGA-II with three
 different strategies to separate the chromosome (disjoint or
 overlapping parts), using a high number of islands. Results show that
 these methods can achieve better quality metrics than the baseline in
 the same amount of time, with larger chromosome lengths.

>>>>

\title{Parallel multi-objective optimization using selective operation application
  islands}
% New title suggestion
% Should co-evolutionary go somewhere? Are they co-evolutionary? - jj
% PABLO: Renaming again to avoid using the co-evolutionary and cooperative

@@

A similar idea is presented here to deal with un-decomposable problems, the selective operation application:
instead of sharing parts of individuals, each processor applies the variation 
operators to a specific subset of the whole individual. We have previously proved 
that extending the length of these subsets, and therefore, sharing some search 
space between islands, implies an improvement in the results.

@@

MOPs usually require a high number of variables, meaning that the MOEAs need to deal with large individuals and spent significant extra time for crossover, mutation and migration. Different authors have proposed methods to divide the decision space (the chromosome) to improve the performance and solution quality. In this aspect, the co-evolution model is a dimension-distributed model where a high-dimensional problem is divided into lower dimensional problems \citep{Gong15models,Tonda12cooperative}, and evolved separately. One example of application of this technique was described in \citep{Kimovski15Parallel}. The method presented in that works involves different workers that evolve sub-populations created and recombined by a master process, which performs different recombination alternatives from the parts returned by worker processes. A high dimensional problem was used to compare these
alternatives. In \citep{Dorronsoro13superlinear}, a distributed
co-evolutionary island model was used.  Although in both papers
significant speedups were attained, only a low number of nodes were
employed (8). However, when the number of islands is increased, the division
of each section of the chromosome becomes smaller, and the scalability
may be affected by obtaining lower quality solutions in the same
amount of time.

@@

A similar approach used to solve this kind of problems is the {\em selective operation application}. In this case, each island deals with the whole chromosome, but only focuses in a fragment of it in the crossover and mutation phase, using the whole chromosome for fitness calculation. This allows to deal with un-decomposable problems.
In our preliminary work \citep{Garcia16hpmoon} we proved
% tried to or actually did it? What did we prove? FERGU: Done
that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time in a multi-objective island-based algorithm.
Moreover, instead of making every island focus in a disjoint subset of the
chromosome, the usage of overlapped (shared) sections of the
chromosome 
can improve the quality of the solutions 
when the number of islands increases. We discovered that the most
adequate overlapping size may vary depending on a relation between the
number of islands and the individual size. However, the experiments
were conducted in a limited experimental system: mono-processor and synchronous island model. This
motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more complete parameter setting. Besides comparing previous methods in this new experimental setup, in this paper we propose
a new method that automatically adapts the size of the overlapped
sections depending on the number of islands to use, comparing it with the previous versions. 
% We have to
                                % emphasize what is actually done. Is
                                % this an addition to the old paper,
                                % or a complete rewrite? - JJ FERGU: rewritten previous paragraph

@@

The hypothesis of this paper is that using overlapped sections of the
chromosome for the selective operation application, calculated depending the number of islands to use, in a
multi-objective island-based algorithm, in a real computational environment, can improve the
quality of the solutions in the same computing time with respect to
the baseline, disjoint and partly overlapped methods. %That was the
                                %hypothesis of the previous
                                %paper. This paper has a new
                                %hypothesis, right? - JJ FERGU: no, this is the hypothesis of this paper (comparing adaptive with partly overlapped), but clarifying it
In order to prove this claim, our new adaptive method has been
compared against different overlapping islands schemes: a
baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a
selective operation application version with disjoint sections and a
fixed-size overlapped version. %What was done in the previous paper?
                               %Are we re-using the results in that
                               %paper? - JJ FERGU: explained before that we are showing new results.
Different benchmark problems and different large number of islands
have been used. Results show that this new technique can improve
different quality indicators in the same amount of time when the
problem size is large.  % Shouldn't this start with "We are trying to
                        % prove..." - JJ FERGU: Already writed in previous paragraph

The rest of the paper is organized as follows: after the State of the Art in distributed and co-evolutionary MOEAs, 
the used methodology and the compared algorithms are described in Section \ref{sec:co-evo}. 
Then, the results of the experiments are presented (Section \ref{sec:res}), Finally, the conclusions and future work are discussed.

@@

% Is this really cooperative co-evolution? - JJ FERGU: You mean the Dorronsoro one? The title says it
Addressing high-dimensional problems with cooperative co-evolution has
also been studied in several works with approaches closer to the one
presented here. The approach to focus on a portion of the chromosome,
as in our overlapped method, was firstly used in the work by
Dorronsoro et al. \citep{Dorronsoro13superlinear}, obtaining
super-linear performance 
in several instances. This approach has also been used by Kimovski et al. \citep{Kimovski15Parallel}, but using a
master-slave method that splits the population into several processors. As in previous work, each node
runs a parallel MOEA that only affects some portion of 
the individuals and the master
process receives all the sub-populations to be combined every certain number of generations. Up to 8 processors
were used in the experimental setup, and several
combination alternatives were compared. The main difference of our work with respect to previous works is that our approach does not 
broadcast all solutions to all islands for recombination, but only one solution to a random island, needing less
communication time. Moreover, Dorronsoro or Kimovsky approaches limited the maximum number of islands to 8, while in this paper we have
used up to 128 islands.

@@

In our previous work \citep{Garcia16hpmoon} we used some of
the aforementioned ideas to compare two different dMOEAs. The first
one divided the chromosome in $P$ sections, being $P$ the number of
islands. Every island $p$ only performed the mutation and crossover in
that part ($p_{th}$) of the chromosome (the selective operation application), while the fitness was
calculated using the whole individual. After a certain number of
generations, individuals were migrated randomly to other islands. The
performance metrics were calculated at the end of the run. The second
method, selective operation application with overlapping islands, used the $p_{th-1}$ and
$p_{th+1}$ sections of each chromosome, besides the $p_{th}$
part. During the same amount of time both methods obtained better
results than a baseline algorithm that dealt with the whole chromosome
in each island for crossover and mutation. We discovered that the
performance using one or another method depends on the number of
sections of the individuals and the number of islands used. This
motivates us to find a new adaptive method to select this number of
sections of the chromosome to use, depending on the number of
islands. Besides, previous experiments were performed on a single
processor synchronous island model with a limited number of islands
(8, 32 and 128). In this paper,  8, 16, 32, 64 and 128 islands have
been used, and this time, the experiments have been run on a real
cluster. Therefore, at the same time we are proposing an adaptive
method to divide the individual search space, we are validating the
previous methods.

@@

\section{Methodology} % This should be called
                                % methodology. The object of the
                                % section is to explain the
                                % methodology used to test the
                                % problem, in order to do that we have
                                % tested different versions that prove
                                % that our methodology works for the
                                % precise reasons we think it works- JJ FERGU: Done, and explained
\label{sec:co-evo}

@@

In this paper we analyse several selective operation application algorithms we have
implemented by using a parallel multi-objective baseline algorithm (B)
as a basis for comparisons. Our proposed methods %methods or method?
                                %Which methods? - JJ
are based in NSGA-II, as almost all the previous works discussed
before
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}. % This is SoA stuff - JJ FERGU: Yes, I added it here againg because a reviewer wasn't very attentive
Therefore, we have used a basic distributed NSGA-II algorithm without
overlapping sections as the baseline (B).

%This probably should deserve a "Algorithm" environment too - JJ FERGU: You mean the LaTeX one? I've used it in the pseudocode figures
This basic distributed algorithms spreads the population among $P$
islands; after a fixed number of generations,
one individual in a given island is migrated to another random island,
thus avoiding to synchronize the global Pareto Front (PF) every
certain number of generations as other methods described in Section 2
do. At the end of the run, the Pareto Fronts of all islands are
aggregated into a new one, and the quality measures are evaluated. 
Different  selective operation application alternatives can be devised to evolve the
subpopulations according to the decision space to be explored by each
islands. Here we will consider three methods in which each island only
performs crossover and mutation in specific sections of the
individuals.

%This algorithm is a regular NSGA-II algorithm distributed along a number $P$ of islands. After a fixed number of generations, one individual is migrated to another random island. At the end of the run, PFs of all islands are aggregated in a new one in order to compute the quality measures. This baseline method has been chosen as it does not require synchronization of the global PF every certain number of generations, as other methods described in Section 2 do.
%% some justification on why this was chosen - JJ PABLO: Added 
%
%% And some liaison to next subsection - JJ
%This method will be compared to different co-evolutionary approaches that are similar to the baseline, with the exception on the decision space to explore in each island.
%Three different co-evolutionary methods have been used. In all these methods, each island only performs crossover and mutation in specific sections of the individuals.

@@

\subsection{Selective operation application with disjoint islands (D)} 
In this approach, each individual of size $L$ is split into $P$ chunks
of size $L/P$. Every island $p$ only performs crossover and mutation
on the $p_{th}$ part of the individuals. Figure \ref{fig:disjoint}
describes this approach.   
%
\begin{figure*}[h!tb]
\centering
\includegraphics[width=12cm]{islandDisjoint.jpg}
\caption{Disjoint algorithm: every island $p$ only modifies the $p_{th}$ components (in grey) of the individuals.}
\label{fig:disjoint}
\end{figure*}

\subsection{Selective operation application with overlapping islands (O)}
This approach is similar to the previous one, but every island also uses the $p+1$ and $p-1$ (module size) chunks of the individual for crossover and migration. Therefore, some kind of overlapping of the crossed and mutated parts exists between islands. Figure \ref{fig:overlapping} shows the affected parts of the individuals in
each island.

@@

\subsection{Adaptive selective operation application with overlapping islands (A)} 
As in the previous method, the sections to address are overlapped, but
instead using one extra section on each side of the $p$ section ($p+1$
and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$),
being $c$ a value depending on the number of islands.
% That's not adaptive. It's simply variable - JJ FERGU: it depends on the number of islands. What term do you suggest?
As a first
approach to automatically calculate this value the results shown in
\citep{Garcia16hpmoon} have been used as a base to obtain $c$. In that
work, the overlapped method ($c=1$) obtained better results when the
number of islands were $>$8. On the contrary, when the number of
islands is small, no overlapping is necessary. So, we have used this
knowledge to create the formula $c=round(0.2*P-1)/2$ to calculate the
extra sections to overlap. Therefore, when $P=8$ then $c=0$
(equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so
on. Figure \ref{fig:adaptive} explains this method.

@@

%EXPLANATION OF THE RESULTS
This can be explained comparing the number of non-dominated solutions in each island and the average number of generations (Table \ref{tab:sols512} and Table \ref{tab:sols2048}). With both chromosome lengths, increasing the number of islands implies more generations with all the methods (logically, as there are less individuals in each island). But also, the selective operation application methods approach to the number of generations with the baseline when increasing the number of islands. However, with $L=2048$ the migration time is enough big to almost not improve the number of generations with respect to the baseline, even in the lower number of islands, as it happens with $L=512$. Therefore, more generations do not necessarily improve the solution of the global PF, but focusing on different elements of the chromosome. As indicated previously, every island is unaware of the other islands PFs, and they are trying to optimize their solutions independently. With respect to the average number of solutions in each island, there is a clear difference in number with the baseline with $L=512$, where this value is in the most of the cases, less than a half. The number of non-dominated solutions also improves a better Spread indicator, where the baseline almost always obtains better values %TENGO QUE COMENTAR MAS LOS RESULTADOS Y ENTENDERLO TODO Y JUSTIFICARLO FINAMENTE

Finally, as happened in \citep{Garcia16hpmoon}, results show that all the quality indicators decrease when the number of islands is increased, as the  sizes of the subpopulations are smaller. This is consistent with the claim by Dorronsoro et al. \citep{Dorronsoro13superlinear}, who found that cooperative co-evolutionary MOEAs work better on bigger populations (more than 100 individuals).

@@

Problems that require high-performance % problems are not high-performance. They
                          % _require_ high performance Fergu: done
 and deal with a large number of decision variables can leverage the
 division of the decision space that parallel and distributed
 algorithms imply. This can be done in dMOEAs by selective operation application, that is, dividing the
 chromosome into different parts, each one modified by a different
 island. This paper compares a baseline distributed NSGA-II with three
 different strategies to separate the chromosome (disjoint or
 overlapping parts), using a high number of islands. Results show that
 these methods can achieve better quality metrics than the baseline in
 the same amount of time, with larger chromosome lengths.
